---
title: "Project Title"
output:
  html_document:
    df_print: paged
    toc: yes
  html_notebook:
    toc: yes
editor_options:
  chunk_output_type: inline
fig_width: 4 
fig_height: 3 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Chapter One

After using lines 1-17 (and changing titles, or experimenting with figure settings), you can start!

```{r}
# Use the Insert tag, to insert chunks of code
print("Hello World")
```

[Here's](https://rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf) a cheat sheet for R Markdown

You can embed YouTube video's. Just go to the YouTube video, and click on *share* followed by *embed*. Copy and paste the code for embedding.

<iframe width="560" height="315" src="https://www.youtube.com/embed/tKUufzpoHDE" title="YouTube video player" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>

After "knitting" this R Markdown file, you will not directly see the video in the thing that pops up on your screen. But an *html* file is created, in the project folder. 

If you click on that file, the [full document](https://rpubs.com/SSM_Research_Center/howto_rmarkdown) opens in your browser. Or you can publish it via, for example, RPubs, to share it with the rest of the world.

## 1.1 Section 1.1

Text

## 1.2 Section 1.2 

### 1.2.1 Subsection 1.2.1

And so on

# 2. Chapter Two

And so on ...

